\subsection{\BtsName}

\begin{expara}

\BtsName{} [-options] [ files ]

\end{expara}

\PrBts{} creates and submits a \ProductName{} batch job from each of the supplied XML files.

XML format job files, usually with suffix \batchjobsuffix, are created when jobs are unqueued with the XML option with \PrBtq{} and similar.

\subsubsection{Options}
The environment variable on which options are supplied is \filename{\BtsVarname} and the environment variable to specify the help file is
\filename{BTRESTCONF}.
\setbkmkprefix{bts}
\explainopt

\cmdoption{v}{verbose}{~}{verbose}

This option causes a message showing the job number of each successfully submitted job to be displayed, whether or not the job file
was created with the verbose option.

\cmdoption{q}{quiet}{~}{quiet}

This option turns off the verbose option for each job submitted. No output is displayed for any job.

\cmdoption{f}{verbose-as-file}{~}{verbasfile}

This option resets the ``verbose'' option so that messages are only displayed if the verbose option is given in the file.

\cmdoption{Q}{host}{host}{host}

This option selects the host to which jobs are to be queued, other than from the host on which they were unqueued from. Specify a single ``-'' to
denote the local host.

\cmdoption{F}{host-as-file}{~}{hostasfile}

Reset the \exampletext{{}-Q} option, so that jobs are queued to the host they originated from.

\cmdoption{C}{cancelled}{~}{cancelled}

This causes the job or jobs to be queued in the ``cancelled'' state rather than whatever state they are set to in the job files.

\cmdoption{N}{normal}{~}{normal}

This causes the job or jobs to be queued in the ``ready to run'' state rather than whatever state they are set to in the job files.

\cmdoption{S}{state-as-file}{~}{stateasfile}

This option resets the \exampletext{{}-C} or \exampletext{{}-N} options so that the jobs are queued in the state that they were set
to in the saved job files.

This is the default if no arguments are specified.

\freezeopts{\filename{\BtsVarname}}{Stop}

\subsubsection{Error Messages}

Appropriate error messages are displayed if the saved job files do not appear to be in XML format, or if \ProductName{} was not built
with the XML library.

Note that job files do not have to have the suffix \batchjobsuffix.


