\subsection{\XbCvlistName}

\begin{expara}

\XbCvlistName{} [ -D dir ] [ -v n ] [ -e n ] [ -s ] [ -f ] var file outfile

\end{expara}

\PrXbCvlist{} converts \ProductName{} variables held in the batch spool
directory to an executable shell script which may be used to re-install
them. This may be useful for backup purposes or for one stage in
upgrade from one release of \ProductName{} to another.

\IfXi{\PrXbCvlist{} understands the format of the saved
variable file for versions of \ProductName{} going
back to release 4, and when presented with a saved file, will attempt
to work out from the format which release it relates to.}

In addition to options, two arguments are always supplied to \PrXbCvlist{}.

\begin{tabular}{l p{14cm}}
Variable list file &
This is the file containing the attributes of the variables, \filename{btsched\_vfile} in the batch spool directory, by
default \spooldir, or as relocated by re-specifying \filename{SPOOLDIR}.\\
& \\
Output file &
This file is created by \PrXbCvlist{} to contain the executable shell script, containing
\PrBtvar{} commands, which may be used to recreate the variables.\\
\end{tabular}

\subsubsection{Options}

Note that this program does not provide for saving options in \configurationfile{} or \homeconfigpath{} files.

\setbkmkprefix{xb-cvlist}

\cmdoption{D}{}{directory}{directory}

This option specifies the source directory for the variables
rather than the current directory. It can be specified as \exampletext{\$SPOOLDIR} or
\exampletext{\$\{SPOOLDIR-\spooldirname\}} etc and the environment and/or \linebreak[3]\masterconfig{} will be
interrogated to interpolate the value of the environment variable given.

If you use this, don't forget to put single quotes around it thus:

\begin{expara}

\XbCvlistName{} -D
{\textquotesingle}\$\{SPOOLDIR-/usr/spool/batch\}{\textquotesingle}
...

\end{expara}

otherwise the shell will try to interpret the \exampletext{\$} construct and not \PrXbCvlist{}.

\cmdoption{e}{}{n}{errorlim}

Tolerate \genericargs{n} errors of the kinds denoted by the other options before giving up trying to convert the file.

\cmdoption{f}{}{}{ignfmt}

Ignore format errors in the saved variables file, up to the limit of errors given by the \exampletext{{}-e} option.

\cmdoption{s}{}{}{ignsize}

Ignore file size errors in the saved variables file (up to the number of total errors given by the \exampletext{{}-e} option.

\IfXi{\cmdoption{v}{}{number}{version}

Tell \PrXbCvlist{} that the variables file is for release number of \ProductName{}, where number
is 4 to 6. This may be necessary where the user file is corrupted and \PrXbCvlist{} cannot guess what is meant.}

